%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer I} % Job title
    {American Express} % Organization
    {Phoenix, AZ} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain a real time financial transaction capture system using Golang, Redis, Cassandra and Kafka.}
        \item {Maintain a scheduler that compiles transactions processed every few minutes for clearing and settlement in the same stack.}
        \item {Leading migrations from the legacy application to our current system for different markets, including the US, Germany, Japan and Australia.}
        \item {Leaded development for APACS40, a payment type allowing the European Market to use American Express cards in stores.}
        \item {Became the deployment champion, assisting in environmental, deployment and production issues ensuring our system has no issues, freeing up my developer's time to code.}
        \item {Use Kibana and Graphana to filter out failed transactions out of the millions processed everyday, isolating and solving issues efficiently.}
        \item {Developed multiple bash and python scripts, automating multiple tasks for our team, increasing efficiency daily.}
        \item {Leading design for new products, taking in the business requirements and turn them into technical stories for our sprints.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {DevOps Engineer} % Job title
  {Texas A\&M University - GeoInnovation Center} % Organization
  {College Station, TX} % Location
  {Apr. 2020 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added unit tests to the geocoder written in C\#, ensuring each function is working as intended.}
        \item {Designed a daily COVID-19 case tracker using data scraped from the NY Times repository with Python. Map was displayed with Angular.}
        \item {Used Postman to automate regression testing for the geocoder, enabling us to keep track of breaking changes while working on the project.}
        \item {Integrated Azure Pipelines into the geocoder, adding CI/CD capabilities for testing and staging environments and increased stability.}
    \end{cvitems}
  }

%---------------------------------------------------------
  % \cventry
  %   {DevOps Engineer} % Job title
  %   {Texas A&M University - GeoInnovation Center} % Organization
  %   {College Station, TX} % Location
  %   {Apr. 2020 - Aug. 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Added unit tests to the geocoder written in C\#, ensuring each function is working as intended.}
  %       % \item {Designed a daily COVID-19 case tracker using data scraped from the NY Times repository with Python. Map was displayed with Angular.}
  %       % \item {Used Postman to automate regression testing for the geocoder, enabling us to keep track of breaking changes while working on the project.}
  %       % \item {Integrated Azure Pipelines into the geocoder, adding CI/CD capabilities for testing and staging environments, increasing stability.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
